### 2025-07-08 index.qmd
20250708 - track chunk execution times

```{r}
#| label: setup
#| include: false

# Global knitr options
knitr::opts_chunk$set(
  time = TRUE,
  message = NA # Show in console, not in rendered output
)

# Null coalescing operator
`%||%` <- function(a, b) if (!is.null(a)) a else b

# Log file setup
log_file <- "chunk-times.txt"
if (file.exists(log_file)) file.remove(log_file)

# Environment to track start times
.chunk_times_env <- new.env()

# Timing hook
knitr::knit_hooks$set(time = function(before, options) {
  label <- options$label %||% "<unnamed>"

  if (before) {
    .chunk_times_env[[label]] <- Sys.time()
  } else {
    start_time <- .chunk_times_env[[label]]
    if (!is.null(start_time)) {
      elapsed <- difftime(Sys.time(), start_time, units = "secs")
      msg <- sprintf("Chunk `%s` ran in %.2f seconds.", label, as.numeric(elapsed))

      # Send message to GitHub Actions log
      message(sprintf("::notice title=Chunk Time::%s", msg))

      # Also save to file
      cat(msg, file = log_file, append = TRUE, sep = "\n")
    }
  }
})
```

>>>>

{{< include _chunk-timing.qmd >}}
